Build Your Own EV: A Rapid Energy-Aware Synthesis of Electric Vehicles

### 2018-07-25 draft.tex
Update revision and response to reviewers

The absolute energy consumption per unit distance does not properly explain how the electric vehicles are well designed. 
Energy per unit curb weight also has an important meaning especially for electric vehicles because the battery weight occupies a significant portion of the total curb weight. 
Owners generally want to have a larger capacity battery despite fuel efficiency thinking the driving range more importantly than fuel efficiency, due to many free charging stations and a low enough electricity price for now. However, such promotion will not last forever, and thus manufacturers cannot take the fuel efficiency lightly. Fuel efficiency directly impacts on the fully-charged range per unit battery capacity.

Tesla Model S series consume more energy per unit distance than other electric vehicles because they have heavier curb weights due to a significantly larger battery capacity. Fig.~\ref{fig:fuel_efficiency}(b) justifies that longer range electric vehicles are generally less fuel efficient. However, Tesla Model S series show a higher energy efficiency per unit curb weight thanks to aggressive deployment of light materials such as aluminum and carbon.  
This implies that use of more light materials is a practically applicable practice for a higher fuel efficiency. Manufacturers do not generally include repair cost in the cost of ownership assuming no accidents. However, deployment of lighter materials potentially increase the total cost of ownership way more than the vehicle price itself due to extremely high repair cost \cite{Repair_cost}. To make a long story short, curb weight is a big matter of electric vehicle fuel efficiency, but use of light materials may significantly increase the potential cost of ownership.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cross-layer power optimization of Cyber-physical systems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have a lesson learned from the battery-operated embedded systems how cross-layer power optimization could push the efficiency of the entire system beyond the limitation of the individual components. Cross-layer power optimization can turn off unused components during runtime without appreciable degradation in the performance as long as the power manager is fully aware of the application context. This may result in virtually equivalent amount of power saving to make the component power close to zero if the active duty ratio of the component is low. Cross-layer system-level power optimization is becoming more and more important as devices and circuit technologies are matured, and the headroom for further optimization is very narrow.

Fortunately, we can see new but strong initiatives for application-aware cross-layer design and management that attempt to reduce energy consumption of Cyber-physical systems by applying algorithms, tools and methodologies relevant to design automation and embedded low-power systems. 
For instance,
%several, hybrid energy storage systems improve efficiency and lifetime without significant increase of the cost~\cite{Kim:JPS14}.  %\cite{Xie:TCAD13, Kim:JPS14}
~\cite{Lin:ICCAD14}
electric vehicles consume a non-negligible amount of battery energy for non-driving power components. Related study optimizes energy for heating, ventilation and air conditioning (HVAC) systems equipped in electric vehicles~\cite{Vatanparvar:DAC15}. %\cite{Vatanparvar:DAC15, Zhao:ICCAD15} 
%Electric vehicle battery packs consist of a large number of battery cells, and it is crucial to optimize the battery pack architectures in terms of capacity, cost and reliability~\cite{Steinhorst:ASPDAC16}. %\cite{Steinhorst:ASPDAC16, Wu:TCAD13}. 
%Electric vehicle battery management systems would better be able to accommodate multiple power sources, provide a good scalability and mitigate cell-to-cell variability. %\cite{Shin:TCAD15, Narayanaswamy:TVLSI17}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cross-layer power optimization of electric vehicles}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Fig.~\ref{fig:GUI} shows a new electric vehicle selection function for non-tech-savvy customers. Customers are supposed to pick an electric vehicle model first, which is subjective to personal preference, but the major difference is customized energy consumption evaluation by a novel rapid energy-aware electric vehicle synthesis algorithm. The rapid synthesis algorithm starts from the customer’s daily life data, which is absolutely non-technical such as the home/work addresses, time to commute, and primary purpose of vehicle (work/leisure.) The result of the synthesis is 1) the powertrain configuration of the electric vehicle such as the traction motor power rating, gearbox ratio and battery capacity, 2) expected vehicle performance (the maximum acceleration, maximum velocity and driving range) and 3) MSRP. The synthesis algorithm allows the customers to try various choices in a short period of time such as the performance and driving range. The resultant energy consumption, the driving range and the required battery capacity to satisfy the driving range are not the OEM (original equipment manufacturers) standard values but the true customer-dependent values.

@@

Fig.~\ref{fig:framework_proposed} illustrates the rapid energy-aware electric vehicle synthesis flow. 
Following the flow in Fig.~\ref{fig:framework_proposed}, the algorithm extracts the required acceleration, top speed and driving range, which become hard constraints for the synthesis. The algorithm finds an electric vehicle powertrain configuration that fulfills the requirements while consuming the least amount of energy for the dedicated driving mission. 
We first compute the generic energy consumption for a given customer-dependent driving profile. This requires running a vehicle simulator, but this is just one-time evaluation unlike the conventional method. The iterative steps basically are the same as the design space exploration like the conventional method by changing the motor power rating, gearbox ratio and the battery capacity discovering the resultant vehicle performance, energy consumption and the driving range. As we already computed the generic energy consumption, the iterative step simply requires multiplication operations instead of running the vehicle simulator. This drastically reduces the computation time. Once again, the resultant energy consumption, the driving range and the required battery capacity to satisfy the driving range are not the OEM standard values but the true customer-dependent values optimized for the given driving mission.

>>>>

The absolute energy consumption per unit distance does not properly explain how the electric vehicles are well designed. 
Energy per unit curb weight also has an important meaning especially for electric vehicles because the battery weight occupies a significant portion of the total curb weight. 
%Owners generally want to have a larger capacity battery despite fuel efficiency thinking the driving range more importantly than fuel efficiency, due to many free charging stations and a low enough electricity price for now. 
\textcolor{red}{Owners generally want to have a larger capacity battery despite low fuel efficiency. They think that the driving range is more important than fuel efficiency due to many free charging stations and a low enough electricity price for now.}
However, such promotion will not last forever, and thus manufacturers cannot take the fuel efficiency lightly. Fuel efficiency directly impacts on the fully-charged range per unit battery capacity.

Tesla Model S series consume more energy per unit distance than other electric vehicles because they have heavier curb weights due to a significantly larger battery capacity. Fig.~\ref{fig:fuel_efficiency}(b) justifies that longer range electric vehicles are generally less fuel efficient. However, Tesla Model S series show a higher energy efficiency per unit curb weight \textcolor{red}{than others (only Tesla Model S series are under the red line in Fig.~\ref{fig:fuel_efficiency}(b))} thanks to aggressive deployment of light materials such as aluminum and carbon.  
This implies that use of more light materials is a practically applicable practice for a higher fuel efficiency. Manufacturers do not generally include repair cost in the cost of ownership assuming no accidents. However, deployment of lighter materials potentially increase the total cost of ownership way more than the vehicle price itself due to extremely high repair cost. %\cite{Repair_cost}. 
To make a long story short, curb weight is a big matter of electric vehicle fuel efficiency, but use of light materials may significantly increase the potential cost of ownership.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Design-Time Optimization of Electric Vehicles}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We have a lesson learned from the battery-operated embedded systems how cross-layer power optimization could push the efficiency of the entire system beyond the limitation of the individual components. Cross-layer power optimization can turn off unused components during runtime without appreciable degradation in the performance as long as the power manager is fully aware of the application context. 
%This may result in virtually equivalent amount of power saving to make the component power close to zero if the active duty ratio of the component is low. Cross-layer system-level power optimization is becoming more and more important as devices and circuit technologies are matured, and the headroom for further optimization is very narrow.

Fortunately, we can see new but strong initiatives for application-aware cross-layer design and management that attempt to reduce energy consumption of Cyber-physical systems by applying algorithms, tools and methodologies relevant to design automation and embedded low-power systems. 
\textcolor{red}{For instance, the hybrid electric vehicles (HEV) improves fuel efficiency and performance but also increase management complexity. the HEV power management policy is optimized using reinforcement learning~\cite{Lin:ICCAD14}.}
Also, electric vehicles consume a non-negligible amount of battery energy for non-driving power components. Related study optimizes energy for heating, ventilation and air conditioning (HVAC) systems equipped in electric vehicles~\cite{Vatanparvar:DAC15}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Cross-layer power optimization of electric vehicles}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Fig.~\ref{fig:GUI} shows a new electric vehicle selection function for non-tech-savvy customers. Customers are supposed to pick an electric vehicle model first, which is subjective to personal preference, but the major difference is customized energy consumption evaluation by a novel rapid energy-aware electric vehicle synthesis algorithm. The rapid synthesis algorithm starts from the customer’s daily life data, which is absolutely non-technical such as the home/work addresses, time to commute, and primary purpose of vehicle (work/leisure.) The result of the synthesis is 1) the powertrain configuration of the electric vehicle such as the traction motor power rating, gearbox ratio and battery capacity, 2) expected vehicle performance (the maximum acceleration, maximum velocity and driving range) and 3) MSRP. The synthesis algorithm allows the customers to try various choices in a short period of time such as the performance and driving range. 
\textcolor{red}{The proposed algorithm does not present only one optimized powertrain specification but suggests various powertrain specifications to the user with the rapid synthesis. This feature allows the user to find powertrain specifications satisfying driving for other purposes besides the commuting.}
The resultant energy consumption, the driving range and the required battery capacity to satisfy the driving range are not the OEM (original equipment manufacturers) standard values but the true customer-dependent values.

@@

Fig.~\ref{fig:framework_proposed} illustrates the rapid energy-aware electric vehicle synthesis flow. 
Following the flow in Fig.~\ref{fig:framework_proposed}, the algorithm extracts the required acceleration, top speed and driving range, which become hard constraints for the synthesis. The algorithm finds an electric vehicle powertrain configuration that fulfills the requirements while consuming the least amount of energy for the dedicated driving mission. 
We first compute the generic energy consumption for a given customer-dependent driving profile, \textcolor{red}{which is synthesized based on road condition, driver preference and driver's tendency (or hard braking, rapid acceleration, etc.)} This requires running a vehicle simulator, but this is just one-time evaluation unlike the conventional method. The iterative steps basically are the same as the design space exploration like the conventional method by changing the motor power rating, gearbox ratio and the battery capacity discovering the resultant vehicle performance, energy consumption and the driving range. As we already computed the generic energy consumption, the iterative step simply requires multiplication operations instead of running the vehicle simulator. This drastically reduces the computation time. Once again, the resultant energy consumption, the driving range and the required battery capacity to satisfy the driving range are not the OEM standard values but the true customer-dependent values optimized for the given driving mission.
